### 2023-01-05 Manuscript/Draft1.Rmd
update manuscript and plotting file

<!-- ```{r linearvsdiffuse, echo=FALSE, message=FALSE, warnings=FALSE, out.width='7in', fig.cap=figcap5} -->
<!-- #knitr::include_graphics(file.path(getwd(),"MS_tables_figs_rev1/final_ms_figs","Figure_5.pdf")) -->
<!-- ``` -->
>>>>>>> fac774b6b2cab2991e9875992ad8ca7eb3de1326

>>>>

<!-- ```{r linearvsdiffuse, echo=FALSE, message=FALSE, warnings=FALSE, out.width='7in', fig.cap=figcap5} -->
<!-- #knitr::include_graphics(file.path(getwd(),"MS_tables_figs_rev1/final_ms_figs","Figure_5.pdf")) -->
<!-- ``` -->
